### 2014-02-20 paper/retrofit.tex
mini ml

\section{Retrofitting languages with IFC}
\label{sec:retrofit}
\cut{

@@

\begin{figure}
\begin{verbatim}
e ::= e e
    | x
    | ref e
    | !e
    | e := e
    | fix e
    | if e then e else e
    | v

v ::= \ x . e
    | #t
    | #f
    | a
\end{verbatim}
\label{fig:ml}
\end{figure}

(Selected rules from evaluation semantics. It's typed in the usual way.)

>>>>

\section{Retrofitting languages with IFC}
\label{sec:retrofit}

We consider language of the form |(S, E, e, -->)|, where |S| is some
global state, |E| is an evaluation context, |e| is an expression in
the language and |-->| is the reduction relation on the state,
evaluation context and expression;
we say expression |e| in context |E| and state |S| reduces to
expression |e'| in context |E'| and state |S'| and write
|conf S (E[e]) --> conf S' (E'[e'])|.

@@

\begin{figure}
\begin{code}
tv   ::= \x.te | true | false | ta
te   ::= tv | x | te te | if te then te else te | ref te | !te | te := te | diverge
tE   ::= tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

te1 ; te2           @= (\x.te2) te1  where  x notmember FV(te2)
let x = te1 in te2  @= (\x.te2) te1
\end{code}

\begin{mathpar}
\inferrule[T-app]
{ } {| conf tS (tE[(\x.te) tv]) --> conf tS (tE[{tv/x} tv]) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (tE[if true then te1 else te2]) --> conf tS (tE[te1]) |}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (tE[if false then te1 else te2]) --> conf tS (tE[te2]) |}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (tE[ref tv]) --> conf tS' (tE[tv]) |}
{| fresh ta |}

\and
\inferrule[T-deref]
{| (ta, tv) member tS |}
{| conf tS (tE[!ta]) --> conf tS (tE[tv]) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (tE[ta := tv]) --> conf tS' (tE[tv]) |}
\end{mathpar}

\caption{Simple ML-like language}
\label{fig:ml}
\end{figure}

\cut{
(Selected rules from evaluation semantics. It's typed in the usual way.)
